### 2021-11-29 README.Rmd

<!-- badges: start -->
[![R-CMD-check-stable](https://github.com/signaturescience/skater/workflows/R-CMD-check-stable/badge.svg)](https://github.com/signaturescience/skater/actions)

[![R-CMD-check-dev](https://github.com/signaturescience/skater/workflows/R-CMD-check-dev/badge.svg)](https://github.com/signaturescience/skater/actions)
<!-- badges: end -->

>>>>

<!-- badges: start -->

[![R-CMD-check-stable](https://github.com/signaturescience/skater/workflows/R-CMD-check-stable/badge.svg)](https://github.com/signaturescience/skater/actions)

[![R-CMD-check-dev](https://github.com/signaturescience/skater/workflows/R-CMD-check-dev/badge.svg)](https://github.com/signaturescience/skater/actions)

<!-- badges: end -->
